\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2025-03-30 Archive/Plots.Rmd

```{r}
library(ggplot2)
ggplot(df, aes(x = Venue, y = RxnTime, group = Venue)) +
  geom_boxplot() +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.05, 0.275),
                            breaks = seq(0.05, 0.275, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2024),
                                              breaks = seq(1999, 2024, 2))
ggsave(filename="Boxplot.pdf", path = "../Manuscript", height = 4, width = 6)
```

>>>>

```{r}
library(ggplot2)
ggplot(df, aes(x = Venue, y = RxnTime, group = Venue)) +
  geom_boxplot() +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.05, 0.275),
                            breaks = seq(0.05, 0.275, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2024),
                                              breaks = seq(1999, 2024, 2))
#ggsave(filename="Boxplot.pdf", path = "../Manuscript", height = 4, width = 6)
```
# Supplementary Womens Boxplot
```{r}
library(tidyverse)
dhw <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "F") |>
  filter(Time != "DNS") |>
  filter(RxnTime > 0) |>
  filter(Event == "100 Hurdles" | Event == "110 Hurdles")
library(ggplot2)
ggplot(dhw, aes(x = Venue, y = RxnTime, group = Venue)) +
  geom_boxplot() +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.05, 0.3),
                            breaks = seq(0.05, 0.3, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(2000,2024),
                                              breaks = seq(2001, 2024, 2))
ggsave(filename="WomensBoxplot.pdf", path = "../Manuscript", height = 4, width = 6)
```

### 2025-03-30 Manuscript/reply.tex

In the revision, we have added explanation about why 100-meter dash
data for both men and wemen were included, while 200-meter dash data
were not included in our analysis in the opening paragraph of Section~2.
The subsequent analyses in the manuscript have been updated with the
expanded datasets.

@@

For the approximately 20 disqualified athletes with positive reaction
times, we examined the impact of including them in the analysis. The
probability of observing a reaction time below 0.1 seconds increased
\jy{Are these based on the expanded dataset or the original dataset?}
\jy{These numbers need to be updated}
\of{Used 2 datasets: both men's dash and hurdles with 2022.  One dataset did not
include DQs the other did. The numbers reflect the supplement results}
slightly from 0.00197 to 0.00276, with similar parameter estimates for
the random effects. Given these results, we opted to include these
observations in the dataset.
\eds{Currently the text in the manuscript suggests we are including a 
sensitivity analysis in the Supplement for the analysis without the positive DQs.
If we are indeed including that, we should mention that here too. (If not, we 
need to remove that statement from the main manuscript.)}

>>>>

In the revision, we have added explanation about why 100-meter dash
data for both men and women were included, while 200-meter dash data
were not included in our analysis in the opening paragraph of Section~2.
The subsequent analyses in the manuscript have been updated with the
expanded datasets.

@@

For the approximately 20 disqualified athletes with positive reaction
times, we examined the impact of including them in the analysis. The
probability of observing a reaction time below 0.1 seconds increased
slightly from 0.00197 to 0.00276, with similar parameter estimates for
the random effects. Given these results, we opted to include these
observations in the dataset presented in the main paper. The analysis without
the positive disqualified reaction times is included in the Section 3 of 
the Supplementary Material.

### 2025-03-30 Manuscript/supp.tex

As an alternative to the methods described in Section 3.1 of the main paper, it
is possible to combine all men's and women's reaction time (RT) data for each of 
the three competition
comparisons.  Thus we shrink our analyses from six to three, but each analysis
is roughly twice as big as previously.
For the 2022 national versus
international comparison, there were 160 RTs from 35
athletes and the asymptotic test result was a p-value of $1.94 \cdot 10^{-7}$.
For the 2019 versus 2022 comparison,
there were 258 RTs from 65 athletes and the asymptotic
test result was a p-value of $3.56 \cdot 10^{-8}$. 
For the 2023 versus 2022 comparison, there were 343 RTs
from 92 athletes and the asymptotic test result was a p-value of
$4.99 \cdot 10^{-12}$.  As a result of the larger sample sizes, the code was
very computationally expensive to run and thus we ran it on a smaller size.  All
three permutation tests had a p-value of $1 \cdot 10^{-5}$, which is the smallest
possible value given the permutation test size of $100,000$.  When taken together
with the asymptotic results, the message becomes very clear. These are all
highly significant test results that show substantial differences in average RT
for athletes competing at multiple championship-level competitions.

@@

Nonetheless, in this section,
we exclude all disqualified RTs to see their effect on the probability of an
extreme RT. We fit an identical model to the generalized Gamma model
presented in Section 3.2.  As in Section 3.2, we considered data from men's dash and
hurdles and include 2022 in our analysis to try and determine how sensitive
our model is to the inclusion/exclusion of these times.

@@

Table~\ref{tab:DQSim_probability} shows the effect of removing disqualified (DQ)
times from the analysis.  The probability of observing extreme RTs is lower when
we remove the 17 observations.  While the probability of observing an extreme
RT is less when we remove disqualified athletes, many of the 
conclusions remain the same: the current standards for disqualification are not
grounded in statistical analysis, and there appear to be unequal standards for men
and women.

>>>>

As an alternative to the methods described in Section 3.1 of the main paper, it
is possible to combine all men's and women's reaction time (RT) data for each of 
the three competition
comparisons.  Thus we shrink our analyses from six to three, but each analysis
is roughly twice as big as previously.
For the 2022 national versus
international comparison, there were 160 RTs from 35
athletes and the asymptotic test result was a p-value of $1.94 \cdot 10^{-7}$.
For the 2019 versus 2022 comparison,
there were 258 RTs from 65 athletes and the asymptotic
test result was a p-value of $3.56 \cdot 10^{-8}$. 
For the 2023 versus 2022 comparison, there were 343 RTs
from 92 athletes and the asymptotic test result was a p-value of
$4.99 \cdot 10^{-12}$.  As a result of the larger sample sizes, the 
permutation-based tests were very computationally expensive to run and so we 
used a smaller number of permutations ($100,000$ instead of $1,000,000$).  All
three permutation tests had a p-value of $1 \cdot 10^{-5}$, which is the smallest
possible value given $100,000$ permutations.  When taken together
with the asymptotic results, the message is very clear. These are all
highly significant test results that show substantial differences in average RT
for athletes competing at multiple championship-level competitions.

@@

Nonetheless, in this section,
we exclude all disqualified RTs to see their effect on the probability of an
extreme RT. We otherwise fit an identical generalized Gamma model to the men's 
dash and hurdles RT data (including 2022), as presented in Section 3.2,
to determine how sensitive our model is to the inclusion/exclusion of these times.

@@

Table~\ref{tab:DQSim_probability} shows the effect of removing disqualified (DQ)
times from the analysis.  The probability of observing extreme RTs is lower when
we remove the 17 observations.  While the probability of observing an extreme
RT is less when we remove the RTs of disqualified athletes, many of the 
conclusions remain the same: the current standards for disqualification are not
grounded in statistical analysis, and there appear to be unequal standards for men
and women.
